---
title: "Lecture09"
author: "Joseph Miller"
date: "2/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read our input data

```{r}
#Save your input data file to a new 'data' directory
fna.data<- "WisconsinCancer.csv"

# Complete the following code to input the data and store as wisc.df
wisc.df<- read.csv(fna.data)
```

# Double check your data

```{r}
head(wisc.df)
```

# Looks like there is a funyy last col"X". Let's check how many samples and features (i.e. patients and cols respectively) there are.

```{r}
# number of patients
nrow(wisc.df)

# number of features
ncol(wisc.df)
```

Change the data. Take cols 3-32 for further analysis (drop x and M/B diagnosis)

```{r}
wisc.data <- wisc.df[,3:32]
head(wisc.data)
```

Add patient ID as row names

```{r}
rownames(wisc.data)<- wisc.df$id

wisc.data
```

Q: how many M vs B diagnosis

```{r}
table(wisc.df$diagnosis)
```

Q: how many features are "_mean" values

```{r}
#colnames(wisc.data)
inds<-grep("_mean", colnames(wisc.data))

length(grep("_mean", colnames(wisc.data)))

colnames(wisc.data)[inds]
```


PCA

```{r}
#colMeans(wisc.data)

round(apply(wisc.data, 2, sd),2)
```

We need some scaling 

## Principal Component Analysis

```{r}
wisc.pr<-prcomp(wisc.data, scale=T)

diagnosis <- as.numeric(wisc.df[,2])

summary(wisc.pr)
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=as.numeric(diagnosis), xlab="PC1", ylab="PC2")
```

```{r}
pr.var<-wisc.pr$sdev^2
sum(pr.var)

w<- pr.var/sum(pr.var) * 100

round(w, 2)

plot(w, main="Scree plot", xlab= "PC", ylab= "Varience", type="o")
```


```{r}

#Axis = flase, allows to make own axis.
#names.arg= paste type of name on x axis
barplot(w, ylab = "Precent of Variance Explained",
     names.arg=paste0("PC",1:length(w)), las=2, axes = FALSE)

axis(2, round(w))
```


```{r}
d<-dist(wisc.pr$x[,c(1,2)])

hd<-hclust(d, method = "ward.D2")
plot(hd)
```


Cut tree into 3 groups/ clusters

```{r}
grp3<- cutree(hd, k=3)
table(grp3, diagnosis)


```


```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=grp3, xlab="PC1", ylab="PC2")
```

Cross tabulation

```{r}
diagnosis<- wisc.df$diagnosis == "M"
table(grp3, diagnosis)
```



```{r}
new.d<-read.csv("https://tinyurl.com/new-samples-CSV")

npc<-predict(wisc.pr, new.d)

plot(wisc.pr$x[,1:2], col=grps)
points(npc[,1], npc[,2], col="blue", pch=16)
```































