---
title: "Class12"
author: "Joseph Miller"
date: "2/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Clean up our protein target structure

First we download a target (i.e. protein receptor) structure from the main PDB database. We will pick PDB ID "1hsg"

```{r}
library(bio3d)
file.name <- get.pdb("1hsg")
```

Extract the protein only segment of this PDB entry and write out a new PDB format file. We will also do the same for the bound ligand.

```{r}
hiv <- read.pdb(file.name)
```

```{r}
hiv
```

Protein extraction from data

```{r}
prot<- trim.pdb(hiv, "protein")
prot
```

```{r}
write.pdb(prot, file="1hsg_protein.pdb")
```

repeat for ligand

```{r}
ligand<- trim.pdb(hiv, "ligand")
ligand
```

```{r}
write.pdb(ligand, file="1hsg_ligand.pdb")
```

alternatively, in line 38 ish, could use prot.file.name<-paste(pdb.code, "_protein.pdb", sep="") then repeat for ligand


## Convert our docking results for viewing in VMD

```{r}
res <- read.pdb("all.pdbqt", multi= TRUE)
res
```

```{r}
write.pdb(res, file="results.pdb")
```


```{r}
# res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
```


```{r}

```















